

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={blue!50!black},
    urlcolor={black}
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}


  \textbf{{\LARGE Priyanshu Singh}} & Email: \href{s.priyanshu.coder@gmail.com}{s.priyanshu.coder@gmail.com}\\
  \underline{\href{https://dev-priyanshu-g4g8.vercel.app/}{Portfolio}} & \underline{\href{https://www.linkedin.com/in/priyanshu-singh-b20073257}{LinkedIn}} \\
  \underline{\href{https://github.com/dev-priyanshu15}{Github: Priyanshu Singh}} & Mobile:~~~+91-969-327-1783 
\end{tabular*}

%-----------EDUCATION-----------------

	    

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {RNS Institute Of Technology}{CGPA: 8.3}
      {Bachelor of Engineering-Information Science And Engineering}{2022 - 2026}
      \vspace{-5pt}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, Java, JavaScript, TypeScript, Golang}
     
    \textbf{Technologies/Frameworks}{: React, Redux, Next.js, Node.js, Express.js, Material-UI, Bootstrap, Tailwind CSS, GraphQL, RESTful API}
     
     \textbf{Databases/Tools}{: MongoDB, PostgreSQL, Redis, Cloudinary, Git, GitHub, CI/CD, Docker, AWS, GitOps,  Socket.io, Linux}
    }}
 \end{itemize}
 \vspace{-10pt}
%-----------Open Source-----------------

%-----------Experience-----------------
\section{Experience and Open Source}
\resumeSubHeadingListStart

  \resumeSubheading
  {\href{https://hacktoberfest.digitalocean.com/}{\underline{Hacktoberfest}}}{October 2024-Nov 2024}
  {Contributor: Open Source}{Remote}
  \resumeItemListStart
  \item Contributed to multiple open-source projects, fixing bugs and adding features in \textbf{React}, \textbf{Node.js}, and \textbf{Python}.
  \item Enhanced documentation and improved the user experience for popular open-source repositories.
  \item Collaborated with maintainers and community members through GitHub, adhering to best practices in version control and code quality.
  \resumeItemListEnd

  \resumeSubheading
  {\href{https://gssoc.in/}{\underline{GSSoC}}}{ October 2024-Present}
  {Contributor: Open Source}{Remote}
  \resumeItemListStart
  \item Participated in the Google Summer of Code (GSSoC) as a contributor to \textit{FOSS} organizations, focusing on \textbf{Web Development} and \textbf{Backend Development}.
  \item Worked on various projects, contributing code for new features, bug fixes, and refactoring the existing codebase.
  \item Gained experience in collaborating with global teams and working with GitHub workflows in open-source environments.
  \resumeItemListEnd

\resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{\textbf{EduSphere} $|$ \emph{Next.js, TypeScript, Node.js, Express.js, MongoDB}
$|$
\textmd{\href{https://github.com/dev-priyanshu15/placement-preparation-app}{\underline{GitHub}}}
}{
\begin{itemize}
\item Developed a placement prep app with courses and assignments using \textit{Next.js}, \textit{TypeScript}, \textit{Node.js}, and \textit{MongoDB}.
\item Integrated secure authentication, payment processing, and an admin dashboard for managing users and content.
\item Implemented real-time notifications and updates to keep users engaged with new courses and assignments.
\item Designed a flexible backend for scalability, ensuring the app can handle large user loads and requests.
\end{itemize}
}

\vspace{-10pt}

\resumeSubItem{\textbf{Music Blockchain App} $|$ \emph{MERN, Smart Contracts, Blockchain}
$|$
\textmd{\href{https://github.com/dev-priyanshu15/blockchain}{\underline{GitHub}}}
}{
\begin{itemize}
\item Built a decentralized music platform using \textit{MERN} and \textit{Ethereum Smart Contracts} for secure interactions.
\item Designed features for content sharing, ratings, and secure blockchain-backed user engagement.
\item Integrated a token-based system for incentivizing content creators and users through rewards.
\item Ensured transparency in transactions by leveraging blockchain, allowing users to verify and track interactions.
\end{itemize}
}

\vspace{-10pt}

\resumeSubItem{\textbf{Neighborhood News App} $|$ \emph{React, Node.js, Express.js, MongoDB}
$|$
\textmd{\href{https://github.com/dev-priyanshu15/news-app}{\underline{GitHub}}}
}{
\begin{itemize}
\item Developed a local news app using \textit{React} and \textit{Node.js} for dynamic content and real-time updates.
\item Implemented secure user authentication for content submission and management.
\item Built a scalable database schema in \textit{MongoDB} for efficient news article storage and retrieval.
\item Optimized the app for performance, ensuring fast loading times even with large volumes of data.
\end{itemize}
}

\vspace{-10pt}

\resumeSubHeadingListEnd
\vspace{-10pt}







%-----------Awards-----------------
\section{Achievements}
\begin{description}[font=$\bullet$]
\item {Placed 1st in \textbf{Ambition Hackathon June 2024} - National Level Hackathon at BIT Bangalore.}
\vspace{-5pt}
\item {Placed 3rd in \textbf{CypherQuest Hackathon Juner 2024} - Dayananda Sagar Academy of Technology.}
\vspace{-5pt}
\item {Placed 3rd in \textbf{Almatron Hackathon June 2024} - Global Academy of Technology.}
\vspace{-5pt}
\item {Participated in \textbf{TechFest November 2023} - National Level Hackathon.}
\end{description}




% %-----------LICENSE AND CERTIFICATIONS-----------------


\vspace{-5pt}



\end{document}
