\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\geometry{margin=0.6in}

\begin{document}

\begin{center}
    {\LARGE \textbf{Priyanshu Singh}} \\
    \href{mailto:s.priyanshu.coder@gmail.com}{s.priyanshu.coder@gmail.com} \\
    +91-969-327-1783 \\
    \href{https://www.linkedin.com/in/priyanshu-singh-b20073257}{LinkedIn: priyanshu-singh} \\
    \href{https://github.com/spriyanshucoder}{GitHub: priyanshu-singh} \\
\end{center}

\section*{Education}
\noindent \textbf{RNS Institute Of Technology} \\
B.E in Information Science and Engineering \hfill 2022 -- 2026 \\
CGPA: 8.3

\section*{Technical Skills}
\begin{itemize}[leftmargin=0.5in]
    \item \textbf{Languages:} C++, Python, Java, JavaScript, HTML, TypeScript
    \item \textbf{Database And Tools:}  MongoDB, PostgreSQL,  Git, Github
    \item \textbf{Frameworks And LIbraries:} NodeJs, Material-UI, Bootstrap, ExpressJs, RESTful API, React, Redux, TailWind
\end{itemize}

\section*{Projects}
\vspace{0.3em}
\textbf{Redux-Shopping-App} \\
\textit{React, Redux, and Material-UI - \href{https://github.com/spriyanshucoder/Redux-Shopping-App}{GitHub}} \\
The Redux Shopping App is a responsive e-commerce platform built with React, Redux, and Material-UI, hosted on Vercel. It features user authentication, product catalog management, a shopping cart, and a seamless checkout process. Additionally, it includes an admin panel for managing products, orders, and users. 

\vspace{0.3em}
\textbf{Flavor-Fusion-App} \\
\textit{ React, Redux, and Material-UI, API - \href{https://github.com/spriyanshucoder/FlavorFusion-App}{GitHub}} \\
The Flavor Fusion App is a responsive recipe discovery and sharing platform built with React, Redux, and Material-UI, hosted on Vercel. It features user accounts, advanced search, meal planning tools, and community-driven recipe submissions. The app offers a seamless experience for browsing, saving, and managing recipes.

\vspace{0.3em}
\textbf{AI-Image-Generator} \\
\textit{React, Node.js, and Express.js., OpenAI's DALL-E  API, Cloudinary - \href{https://github.com/spriyanshucoder/AI-IMAGE-GENERATOR.}{GitHub}} \\
AI Image Generator is a web application that uses OpenAI's DALL-E model to generate images based on user input. The application is built with the MERN stack, Tailwind CSS for the frontend, and uses Cloudinary for cloud-based image storage.

\vspace{0.3em}
\textbf{Object-Detection} \\
\textit{Arduino - \href{https://github.com/spriyanshucoder}{GitHub}} \\
Implementing object detection with Arduino involves using sensors like ultrasonic or infrared to detect objects, controlling motors based on sensor inputs for movement, and potentially integrating a camera module for advanced detection capabilities using image processing libraries like OpenCV.

\section*{Achievements}
\textbf{Techfest-Nov 2023, Bangalore} \hfill November 2023 \\
Placed Top 10 Among 48 other teams in Techfest Coding Competetion 2023


\section*{Hobbies}
\textbf{Open-Source-Contribution} \\
Participate in hackathons focused on open-source technologies, showcasing problem-solving skills, creativity, and the ability to collaborate effectively under pressure.

%\vspace{0.3em}
\section*{Mentorship at RNSIT} \\
Member of cybotryx multidisciplinary team of
robotics club from RNSIT

\end{document}
